### 2018-03-12 Writing/Thesis/content/chapter-conclusion.tex
integrate comments part four

% Summary of findings and limitations: what has been covered LIMITATION: SMALL DATA SETS ESP!!
The evaluation showed a significant advantage regarding Kendall's rank correlation coefficient for all tested methods in comparison to the best algorithm baseline, except instance based label ranking in the standard configuration and label ranking by pairwise comparison for the full meta data. However, regarding the practically possibly more important measure of best three loss, only the three regression based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage. When evaluating best three loss on reduced meta data that does not incorporate probing, although the evaluated data indicates a slight advantage of those same regression models over the baseline still, it is not statistically significant anymore. Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the best three loss and loss for both evaluation on the full and reduced meta data. Thus it can be concluded that in general, a regression-based approach seems to be more promising than a preference-based approach, but is not better than the baseline regarding the best three loss when evaluated on the selected meta data without probing. Out of the regression-based variants, random forest seems to be the most promising one.

@@

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable. An effect on the time and quality of predictions for larger data sets would have to be examined still.

@@

% Auto fitting
Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuarcy, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools like AUTOWEKA \cite{thornton2013auto} or AUTO-SKLEARN \cite{feurer2015efficient}, or even using a whole pipeline prediction tool, for example ML-Plan \cite{wever2017automatic} or the RECIPE framework \cite{DBLP:conf/eurogp/SaPOP17}.

>>>>

% Summary of findings and limitations: what has been covered LIMITATION: SMALL DATA SETS ESP!!
The evaluation showed a significant advantage regarding Kendall's rank correlation coefficient for all tested methods in comparison to the best algorithm baseline, with the exception of the InstanceBased ranker in the standard configuration and the PairwiseComparison ranker for the full meta data. However, regarding the practically possibly more important measure of B3L, only the three regression-based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage. When evaluating B3L on reduced meta data that does not incorporate probing, although the evaluated data indicates a slight advantage of those same regression models over the baseline still, it is not statistically significant anymore. Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the B3L and loss for both evaluation on the full and reduced meta data. Thus it can be concluded that in general, a regression-based approach seems to be more promising than a preference-based approach, but is not better than the baseline regarding the B3L when evaluated on the selected meta data without probing. Furthermore, since the regression-based approach shows an advantage over the preference-based approach in respect to the problem considered in this thesis, one can conclude, that here, the preference-based approach generalizes too much. The additional information available to the regression-based models, the performance values of classifiers, seems to pose an advantage over the abstraction of only considering rankings of classifiers in this case. Out of the regression-based variants, the RandomForest ranker seems to be the most promising one.

@@

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding B3L when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable. An effect on the time and quality of predictions for larger data sets would have to be examined still.

@@

% Auto fitting
Depending on the fact whether one is willing to trade off longer build and prediction times for improved accuracy, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools like AUTOWEKA \cite{thornton2013auto} or AUTO-SKLEARN \cite{feurer2015efficient}, or even using a whole pipeline prediction tool, for example ML-Plan \cite{wever2017automatic} or the RECIPE framework \cite{DBLP:conf/eurogp/SaPOP17}.

### 2018-03-12 Writing/Thesis/content/chapter-evaluation.tex
integrate comments part four

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}. These include the Kendall rank correlation coefficient, performance loss and best three loss regarding classifier performance. For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U. The regression-based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

@@

% How find best version of preference and regression ranker
Furthermore, four alternatives were selected for a regression-based and preference-based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression-based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking. As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance-based label ranking, three different configurations were evaluated, the default configurations and two custom ones. For the first customization, the rank aggregation algorithm used by the label ranker was set to Kemeny-Young. For the second customization, additionally, the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), was set to the square root of the number of instances in the training data set. All of the described rankers are included in an overview in Table \ref{tab:methods}. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others.

@@

Table \ref{tab:evaluationResults} shows the results of the evaluation, with the best mean values and significant differences emphasized as described in the caption of the table. When looking at these results, it must first be noted that positive findings regarding the Kendall rank correlation can be reported. For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults} which shows the results of the significance tests, with random forest having the highest correlation of 0.495. In contrast, the two approaches that did not overtake the baseline, instance based label ranking in the default configuration and label ranking by pairwise comparison, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches. Regarding performance loss, only linear regression and random forest show a significant advantage, with all label ranking approaches except for instance based label ranking having a significant disadvantage in contrast. Moving on to best three loss, the picture largely remains the same, except that surprisingly, REPTree now also has a significant advantage over the baseline. The lowest value here is achieved by random forest with a best three loss of 1.308, in comparison to 2.440 for the best algorithm baseline. These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual best three loss values on the data sets.

As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other. From Table \ref{tab:evaluationResults} it is clear that the regression rankers are superior to the preference rankers, and this advantage is significant, as the weakest of the regression rankers, REPTree, is still significantly better than the strongest label ranking approach, instance based label ranking with Kemeny-Young rank aggregation ($p \approx 4.305E-6$). Out of the four regression rankers, three approaches are furthermore significantly better than REPTree.

Compared to the evaluation on the full set of meta data, the results on the reduced set without probing are less distinctive. For the Kendall Rank correlation, linear regression, M5P and random forest are significantly better than the baseline, and for label ranking, both of the instance based approaches with non-default parameters as well, while the other label ranking approaches are significantly worse than the baseline. In total, random forest is still the best alternative with a correlation of 0.439, slightly worse than the correlation achieved on the full meta data. For both loss measures however, while the disadvantages of the label ranking approaches remain, none of the eight alternatives achieves a significantly better loss or best three loss than the baseline anymore.

With reduced meta data, out of the alternatives that pose a significant advantage compared to the baseline, only random forest is significantly better than all other approaches, the others are not significantly different. With loss and best three loss, no such statement can be made.

@@

\tikzsetnextfilename{LossGraphics}
\begin{figure}
%\pgfplotsset{width=\textwidth}
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
	title=regular scale,
	height=\textwidth,
	width=\textwidth,
	ylabel={BestThreeLoss}, 
	xlabel={Data Set},
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
\begin{tikzpicture}
\begin{axis}[
	title=log scale (base 2),
	height=\textwidth,
	width=\textwidth,
	ylabel={BestThreeLoss}, 
	xlabel={Data Set},
	ymode=log,
	log basis y={2}
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}
}
\caption{The best three loss for the baseline compared to the random forest ranker (full meta data).}
\label{fig:lossGraphics}
\end{figure}

@@

Because the ranking itself is implemented as a means of speeding up the process of algorithm selection, the time it takes to rank is not negligible. The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}. Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible. The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves. However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker. The Random Forest ranker, for example, is the ranker with the highest build time (apart from Pairwise Comparison), and also with the rankings of the generally highest quality. But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds. Furthermore, while the build times are higher, these are not as important due to the fact that each model only needs to be trained once. Although in a real-world scenario, calculation times for meta features also have to be taken into account when ranking, which therefore will be discussed in the following paragraph.

@@

Further insights to be noted are the accuracies predicted for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline. The accuracy of the predictions achieved by the regression based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively. The first thing that attracts attention in this table is the absurdly high values for Linear Regression and M5P, however, these are all caused by the very high maximum value on one data set with id 685. If these extreme maxima remain out of consideration for Linear Regression and M5P (the other algorithms do not have this problem) more reasonable values are obtained. For M5P, on the full meta data the new maximum is 311.526, mean 8.127 and standard deviation 18.407; on the reduced meta data it is a maximum of 474.692, mean 15.444 and standard deviation 27.433. For Linear Regression, on the full meta data the new maximum is 142.996, mean 9.281 and standard deviation 8.438; on the reduced meta data it is a maximum of 131.456, mean 14.351 and standard deviation 10.299. However, these values are still worse than the ones obtained for the Random Forest and REPTree variants. It comes as little surprise that the Random Forest Ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful. The usefulness is dependent on the task these predictions would be used for and whether it requires very accurate predictions of performance values.

@@

The second interesting thing to consider is the ranking which is created by the best algorithm baseline. This ranking constitutes meta-knowledge about the learning process itself in that it shows which algorithms are generally a good choice for many data sets. This ranking is depicted in Table \ref{tab:bestAlgorithmRanking}. The table is to be read top to bottom; of the 22 algorithms, the algorithm in the i-th row is placed first on most data sets when compared to the next 22-i algorithms. The associated number represents the number of data sets on which the algorithm was placed first. It is, however, not a particularly surprising result, as for example the placement of Random Forest as the first algorithm was to be expected. Random Forest is a learning algorithm that is known to often deliver good performances, which was proven again in the results discussed previously - out of the reviewed ranking approaches, Random Forest was the best choice.

>>>>

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{sec:fundamentals}. These include the Kendall rank correlation coefficient, performance loss and B3L regarding classifier performance. The measure chosen for the performance values here is the \textit{predictive accuracy} of a classifier, meaning the number of correctly classified instances in a data set. For all three measures, it is computed whether any difference in performance is significant, by means of the p-value for the Mann-Whitney U. The regression-based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

@@

% How find best version of preference and regression ranker
Furthermore, four alternatives were selected for a regression-based and preference-based alternative each, to get a general idea of how well the respective approach might be suited for the problem. For the regression-based approach, the algorithms chosen were random forest, REPTree, M5P, and linear regression. For all of them, the WEKA implemenation \cite{hall2009weka} was used, and the algorithms where used with the standard hyperparameters set by WEKA. As the preference-based ranking falls under the category of label ranking, and in the jPL-framework, which was used for the implementation of the label ranking algorithms and data set representations, only two alternatives for label ranking are implemented \cite{intelligent2017jpl}, the other two alternatives were generated by modifying the hyperparameters. The implemented alternatives are label ranking by pairwise comparison and instance-based label ranking. As in early tests it became apparent that the instance-based approach might hold more potential, for label ranking by pairwise comparison, only the default configuration dictated by jPL was used. For instance-based label ranking, three different configurations were evaluated, the default configurations and two custom ones. For the first customization, the rank aggregation algorithm used by the label ranker was set to Kemeny-Young. For the second customization, additionally, the number of neighbors of the base learner of the label ranker, namely k nearest neighbor (kNN), was set to the square root of the number of instances in the training data set. All of the described rankers are included in an overview in Table \ref{tab:methods}. In the following section, these eight variants are compared with the baseline and oracle mentioned in the previous section, and among each others. They are referenced by the names in Table \ref{tab:methods} to avoid confusion between the ranker and the learning algorithm it is based on.

@@

Table \ref{tab:evaluationResults} shows the results of the evaluation regarding the accuracy of returned rankings, with the best mean values and significant differences emphasized as described in the caption of the table. When looking at these results, it must first be noted that positive findings regarding the Kendall rank correlation can be reported. For the full set of meta data, six out of the eight implemented alternatives outperform the baseline, all of them significantly, as can be learned from Table \ref{tab:significanceResults}, which shows the results of the significance tests according to the p-value for the Mann-Whitney U. Of all rankers, RandomForest has the highest rank correlation with a value of 0.495. In contrast, the two approaches that did not overtake the baseline, the InstanceBased ranker in the default configuration and the PairwiseComparison ranker, show a significant disadvantage compared to the baseline, and thus also compared to the other ranking approaches. Especially the latter approach has a very low rank correlation, that with a mean value of 0.014 shows almost no correlation with the correct ranking. Regarding performance loss, only the LinearRegression and RandomForest ranker show a significant advantage, with all label ranking approaches except for the InstanceBased ranker with Kemeny-Young rank aggregation having a significant disadvantage in contrast. Here, an advantage of the regression-based approach in general is indicated, although the best value with a loss of 3.097 (achieved by the RandomForest ranker) is still fairly high, depending on the data set one considers. Moving on to B3L, the picture largely remains the same, except that surprisingly, the REPTree ranker now also has a significant advantage over the baseline. The lowest value here again is achieved by the RandomForest ranker with a mean B3L of 1.308, in comparison to 2.440 for the best algorithm baseline. These values are illustrated in Figure \ref{fig:lossGraphics}, with a scatter plot for individual B3L values on the data sets.

As for the rank correlation most of the rankers had a significant advantage over the baseline, it is interesting to compare them among each other. From Table \ref{tab:evaluationResults} it is clear that the regression-based rankers are superior to the preference-based rankers, and this advantage is significant, as the weakest of the regression rankers, the REPTree ranker, is still significantly better than the strongest label ranking approach, the InstanceBased ranker with Kemeny-Young rank aggregation ($p \approx 4.305E-6$). Out of the four regression rankers, three approaches are furthermore significantly better than the REPTree ranker.

Compared to the evaluation on the full set of meta data, the results on the reduced set without probing are less distinctive. For the Kendall Rank correlation, the LinearRegression, M5P and RandomForest rankers are significantly better than the baseline, and for label ranking, both of the InstanceBased approaches with non-default parameters as well, while the other label ranking approaches are significantly worse than the baseline. In total, the RandomForest ranker is still the best alternative with a correlation of 0.439, slightly worse than the correlation achieved on the full meta data. For both loss measures however, while the disadvantages of the label ranking approaches remain, none of the eight alternatives achieves a significantly better loss or B3L than the baseline anymore.

Again, the different approaches can be compared among each other. With reduced meta data, out of the alternatives that pose a significant advantage compared to the baseline, only the RandomForest ranker is significantly better than all other approaches, the others are not significantly different. With loss and B3L, no such statement can be made.

Further interesting points can be observed. First, in Table \ref{tab:evaluationResults} one can see that for the loss and B3L, often, rankers have a similar values. Second, the performance of the preference-based rankers does not differ very much, whether full meta data or reduced meta data was used in the evaluation. While, for example, Kendall's Rank correlation for the LinearRegression ranker is 0.473 for full meta data, it is noticeably lower for reduced meta data with a value of 0.350. On the other hand, the correlation coefficient for the InstanceBased rankers in all configurations does not change at all when removing meta features that involve probing.

@@

\tikzsetnextfilename{LossGraphics}
\begin{figure}
%\pgfplotsset{width=\textwidth}
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
	title=regular scale,
	height=\textwidth,
	width=\textwidth,
	ylabel={B3L}, 
	xlabel={Data Set},
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
\begin{tikzpicture}
\begin{axis}[
	title=log scale (base 2),
	height=\textwidth,
	width=\textwidth,
	ylabel={B3L}, 
	xlabel={Data Set},
	ymode=log,
	log basis y={2}
]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{0};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}
}
\caption{The B3L for the baseline compared to the random forest ranker (full meta data).}
\label{fig:lossGraphics}
\end{figure}

@@

Because the ranking itself is implemented as a means of speeding up the process of algorithm selection, the time it takes to rank is not negligible. The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}. Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible. The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves. However, it is notable that while the PairwiseComparison ranker was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker. The RandomForest ranker, for example, is the ranker with the highest build time (apart from the PairwiseComparison ranker), and also with the rankings of the generally highest quality. But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds. Furthermore, while the build times are higher, these are not as important due to the fact that each model only needs to be trained once. Although in a real-world scenario, calculation times for meta features also have to be taken into account when ranking, which therefore will be discussed in the following paragraph.

@@

Further insights to be noted are the accuracies predicted for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline. The accuracy of the predictions achieved by the regression-based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively. The first thing that attracts attention in this table is the absurdly high values for the LinearRegression and M5P rankers, however, these are all caused by the very high maximum value on one data set with id 685 on OpenML. If these extreme maxima remain out of consideration for the LinearRegression and M5P ranker (the other algorithms do not have this problem) more reasonable values are obtained. For the M5P ranker, on the full meta data the new maximum is 311.526, mean 8.127 and standard deviation 18.407; on the reduced meta data it is a maximum of 474.692, mean 15.444 and standard deviation 27.433. For the LinearRegression ranker, on the full meta data the new maximum is 142.996, mean 9.281 and standard deviation 8.438; on the reduced meta data it is a maximum of 131.456, mean 14.351 and standard deviation 10.299. However, these values are still worse than the ones obtained for the RandomForest and REPTree variants. It comes as little surprise that the RandomForest ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful. This is especially the case, since in addition to a relatively high mean, the standard deviation is rather high as well in all observed variants. The usefulness of the tool to predict performance values is therefore dependent on the task these predictions would be utilized for and whether it requires very accurate predictions of performance values. On the other hand, judging by the fact that the regression-based approach shows to be superior to the preference-based approach, these imperfect predictions seem still seem to be accurate enough to result in a rather good ranking.

@@

The second interesting thing to consider is the ranking which is created by the best algorithm baseline. This ranking constitutes meta-knowledge about the learning process itself in that it shows which algorithms are generally a good choice for many data sets. This ranking is depicted in Table \ref{tab:bestAlgorithmRanking}. The table is to be read top to bottom; of the 22 algorithms, the algorithm in the i-th row is placed first on most data sets when compared to the next 22-i algorithms. The associated number represents the number of data sets on which the algorithm was placed first. It is, however, not a particularly surprising result, as for example the placement of random forest as the first algorithm, and ZeroR in the lower ranks was to be expected. Random forest is a learning algorithm that is known to often deliver good performances, which was proven again in the results discussed previously - out of the reviewed ranking approaches, the RandomForest ranker was the best choice. On the other hand, ZeroR is a simple classifier often used as a baseline, that predicts a static value based on the majority class (or average numeric value of the target feature) \cite{devasena2011effectiveness}.
